Trends of SDR in Thessaloniki

### 2023-07-02 Article.Rmd
Commit 2023-07-02 20:17

<!-- time span -->
The SDR is equivalent to the whole sky Global radiation (or Global Horizontal Irradiance, GHI), and was obtained with a horizontal leveled, CM-21 pyranometer, from 
<!-- \mbox{ -->
`r min(ALL_1_daily_DESEAS$Date)`
<!-- } -->
to
<!-- \mbox{ -->
`r max(ALL_1_daily_DESEAS$Date)`.
<!-- }. -->
Also, we have measurements of direct beam radiation (DNI) obtained by a collocated CHP-1 pyrheliometer, from 
<!-- \mbox{ -->
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`
<!-- } -->
to
<!-- \mbox{ -->
`r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.
<!-- }. -->
Although, we performed similar analysis to DNI as for SDR, due to the sorter duration of the data, the results are not presented here, as they lack the appropriate statistical significance.

Moreover, the DNI was used as auxiliary data, with the clear sky identification algorithm (CSid), to aid with the selection of the appropriate thresholds. 
We have to note that, despite the capability of the CSid to use the DNI as an characterization parameter,

.... wi dindnt use it  .....

but was not used as indicator of clear sky instances

Location

The SDR data used in this study cover the period from January 1993 to March 2011, and were measured with a Kipp & Zonen CM-21 pyranometer operating continuously at the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki ( $40^\circ38'$N, $22^\circ57'$E, 80 m above sea level). The monitoring site is located
near the city centre. The horizon is clear of obstruc-
◦ ◦
tions except for the azimuth angles between 35 and 120where obstacles of up to 10 elevation block the direct
irradiance in the morning for SZA larger than 80 .
These data points were excluded from the analysis, as

Instruments and callibrations

relation to aerosols

Northern Greece has been selected because
it is well known to be located at the crossroads of aerosols and
various pollutants pathways originating in central and Eastern
Europe (Lelieveld et al., 2002; Zerefos et al., 2002). Thessa-
loniki, the major city in northern Greece, lies along the exit of air
pollutants from Europe, in the path of the prevailing long-range
transport (LRT) trajectories, as we move from central and east-
ern Europe to the Mediterranean (Zerefos et. al., 2002). On the

...

...

<!-- ## Preparation. -->

There are three distinct steps to the creation of this dataset:
a) the acquisition of radiation measurements from the sensors, 
b) a radiation data quality check, and 
c) the identification of "clear sky" conditions from the radiometric data
d) data aggregation and trend analysis.

<!-- ### Acquisition of radiometric data. -->

<!-- measurement -->
For the acquisition of radiometric data,
the signal of the broadband instruments is sampled with a rate of $1 \text{Hz}$. The mean and standard deviation values are recorded for every minute.
<!-- dark correction -->
The measurements are corrected for the zero offset of the instrument signal.
As reference of the "dark signal" is used the Sun elevation angle bellow $-10^\circ$, for a period of $3 \text{h}$.
<!-- physical quantities -->
The signal is converted to radiation flux, using a ramped value of the instrument sensitivity, derived from the eight laboratory calibrations of the instrument, during the study period.

<!-- ### Radiation data quality check -->
<!-- The radiation quality is assured with a manual screening, aided by an automatic assessment process. -->
<!-- screening -->
A manual screening is performed, to remove inconsistencies and erroneous recordings, that can occur randomly or systematically, during the long continuous operation of the instrument.
<!-- Quality assurance -->
The manual screening is aided by a radiation data quality assurance procedure, adjusted for this site, based on methods of Long and Shi\ [@Long2008a ; @Long2006].
Thus, problematic recordings have been excluded from further processing. 
Although it is not possible to detect all the bad data, the large number of data and the aggregation scheme we use, can provide us with accurate radiometric measurements, for the scope of this study.

## Clear sky identification

@@

<!-- basic concepts -->
Our method to characterize the sky conditions and the definition of each sky condition has some subjectivity.
The algorithm was calibrated with the main focus to identify the presence of clouds on the sky dome, although there are marginal cases that there will be false positives or false negatives identifications.

@@

<!-- 1. MeanVIP -->
### Mean value of irradiance during the time period.

@@

<!-- 2. MaxVIP -->
### Max value of irradiance during the time period.

@@

<!-- 3. VIL -->
### Variability in irradiance by line length.

@@

<!-- 4. VCT -->
### Variance of Changes in the Time series.

@@

@@

<!-- 5. VSM -->
### Variability in the Shape of the irradiance Measurements.

@@

<!-- ### Clear sky ID -->
In order to estimate the effect of the clouds on the SDR we created three datasets, by characterizing each one-minute measurement with a corresponding sky condition. 
The all-sky conditions, containing all the valid measurements. 
The clear-sky conditions data, where we have inferred that the sky was almost clear of clouds, and the remainder part the data as cloudy sky conditions data (cloud-sky). 
To identify the clear-sky conditions we used the method proposed by @Long2000 and by @Reno2016, that was adapted and configured for the site.
<!-- CS subjectivity -->
We have to note, that the definition of what constitutes as clear or cloudy sky, has some subjectivity, due to the used method of characterization.
As a result, the details of the definition are site specific, it relies on a combination of threshold of comparisons with ideal actinometric models and statistics on different signal behavior.

## Data and data selection.

>>>>

<!-- time span -->
The SDR is equivalent to the whole sky Global radiation (or Global Horizontal Irradiance, GHI), and was obtained with a horizontal leveled, CM-21 pyranometer, from 
<!-- \mbox{ -->
`r min(ALL_1_daily_DESEAS$Date)`
<!-- } -->
to
<!-- \mbox{ -->
`r max(ALL_1_daily_DESEAS$Date)`.
<!-- }. -->
Also, we have measurements of direct beam radiation (DNI) obtained by a collocated CHP-1 pyrheliometer, from 
<!-- \mbox{ -->
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`
<!-- } -->
to
<!-- \mbox{ -->
`r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.
<!-- }. -->
Although, we performed a similar analysis to the DNI as for the SDR, the results are not presented here, as they lack the appropriate statistical significance, due to the sorter duration of the data.
Moreover, the DNI was used as auxiliary data, with the clear sky identification algorithm (CSid), to aid with the selection of the appropriate thresholds. 
We have to note also, that despite the capability of the CSid to use the DNI as an characterization parameter, we haven't use it, to avoid any selection bias due to unequal availability of measurements.

<!-- Location -->

The SDR data were measured with a Kipp & Zonen CM-21 pyranometer operating continuously at the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki ($40^\circ38'$N, $22^\circ57'$E, 80m a.s.l.).
The monitoring site is located near the city centre.
During the study period the CM-21 pyranometer has been independently calibrated four times.
<!-- Preparation. -->
There are three distinct steps to the creation of this dataset:
a) the acquisition of radiation measurements from the sensors, 
b) a radiation data quality check, and 
c) the identification of "clear sky" conditions from the radiometric data
d) data aggregation and trend analysis.

<!--
The horizon is clear of obstructions except for the azimuth angles between 35 and 120 where obstacles of up to 10 elevation block the direct irradiance in the morning for SZA larger than 80.  These data points were excluded from the analysis, as
-->

<!-- Zerefos

Northern Greece has been selected because it is well known to be located at the crossroads of aerosols and various pollutants pathways originating in central and Eastern
Europe (Lelieveld et al., 2002; Zerefos et al., 2002). Thessa-
loniki, the major city in northern Greece, lies along the exit of air
pollutants from Europe, in the path of the prevailing long-range
transport (LRT) trajectories, as we move from central and east-
ern Europe to the Mediterranean (Zerefos et. al., 2002). On the
-->

<!-- a) Acquisition -->
For the acquisition of radiometric data,
the signal of the broadband instruments is sampled with a rate of $1 \text{Hz}$. The mean and its standard deviation are recorded for every minute.
<!-- dark correction -->
The measurements are corrected for the zero offset of the instrument signal.
As reference of the "dark signal" is used the Sun elevation angle bellow $-10^\circ$, for a period of $3 \text{h}$.
<!-- physical quantities -->
The signal is converted to radiation flux, using a ramped value of the instrument sensitivity, derived from the eight laboratory calibrations of the instrument, during the study period.

<!-- b) Radiation data quality check -->
<!-- The radiation quality is assured with a manual screening, aided by an automatic assessment process. -->
<!-- screening -->
A manual screening was performed, to remove inconsistencies and erroneous recordings, that can occur randomly or systematically, during the long continuous operation of the instrument.
<!-- Quality assurance -->
The manual screening is aided by a radiation data quality assurance procedure, adjusted for this site, based on methods of Long and Shi\ [-@Long2008a; -@Long2006].
Thus, problematic recordings have been excluded from further processing. 
Although it is not possible to detect all the bad data, the large number of data and the aggregation scheme we use, can provide us with accurate radiometric measurements, for the scope of this study.

<!-- c) Clear sky identification -->
In order to estimate the effect of the clouds on the SDR, we created three datasets, by characterizing each one-minute measurement with a corresponding sky condition. 
The all-sky conditions, containing all the valid measurements. 
The clear-sky conditions data, correspond to data where we have inferred that the sky was almost clear of clouds, and the remainder part the data was characterized with cloud sky conditions (cloud-sky). 
To identify the clear-sky conditions we used the method proposed by @Long2000 and by @Reno2016, that was adapted and configured for the site.

cite iterative process

@@

<!-- CS subjectivity -->
We have to note, that the definition of what constitutes as clear or cloudy sky, has some subjectivity, due to the used method of characterization.
As a result, the details of the definition are site specific, it relies on a combination of threshold of comparisons with ideal actinometric models and statistics on different signal behavior.

<!-- basic concepts -->
The algorithm was calibrated with the main focus to identify the presence of clouds on the sky dome, although there are marginal cases that there will be false positives or false negatives identifications.

@@

<!-- 1. MeanVIP -->
<!-- ### Mean value of irradiance during the time period. -->

@@

<!-- 2. MaxVIP -->
<!-- ### Max value of irradiance during the time period. -->

@@

<!-- 3. VIL -->
<!-- ### Variability in irradiance by line length. -->

@@

<!-- 4. VCT -->
<!-- ### Variance of Changes in the Time series. -->

@@

\begin{equation}
s_i = \frac{\text{SDR}_{i+1} - \text{SDR}_{i}}{t_{i+1} - t_i}, \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VCT1} \\
\bar{s} = \frac{1}{n-1} \sum_{i=1}^{n-1} s_i \label{eq:VCT2} \\
\sigma_i = \frac {\sqrt{\frac{1}{n-1} \sum_{i=1}^{n-1} \left( s_i - \bar{s} \right)^2} } {\bar{G_i}} \label{eq:VCT3}
\end{equation}

@@

<!-- 5. VSM -->
<!-- ### Variability in the Shape of the irradiance Measurements. -->

@@
